pyTopoComplexity: A Python package for topographic complexity analysis

### 2024-08-18 JOSS/paper.rmd
Add files via upload

**pyTopoComplexity** is a Python package that provides a computationally efficient and highly 
customizable implementation of three methods for quantifying topographic complexity. 
These methods include two-dimensional continuous wavelet 
transform (2D-CWT) analysis, fractal dimension estimation, and rugosity index calculation across 
various spatial scales. This package addresses the scarcity of open-source software for these 
sophisticated methods, which are crucial in modern terrain analysis, and facilitates data 
comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComlexity.git), 
we also include a Jupyter Notebook file that integrates components from the Python-based 
surface-process modeling platform **Landlab** [@Hobley2017]. This allows researchers to 
simulate the smoothing of topography over time through terrestrial nonlinear hillslope 
diffusion processes. By combining these features, **pyTopoComplexity** advances the toolset 
available to researchers for measuring and simulating the time-dependent persistence of 
topographic complexity signatures against environmental forces on terrain surfaces.

@@

Here, $\mathbf{S} = -\nabla z$ represents the downslope topographic gradient, and $S$ is its magnitude. The parameter $K$ is a diffusion-like 
transport coefficient with dimensions of length squared per time. The simulation also incorporates the critical slope gradient ($S_c$) to 
ensure numerical stability and prevent the numerical instability when $S = S_c$. $N$ denotes the number of terms in the Taylor 
expansion, while $i$ specifies the number of additional terms included. If $N = 1$, the expression simplifies to linear diffusion [@Culling1963]. 
The default is set to $N = 2$ that gives the behavior described in @Ganti2012 as an approximation of the nonlinear diffusion.

>>>>

**pyTopoComplexity** is a Python package that provides a computationally efficient and customizable 
implementation of three methods for quantifying topographic complexity. These methods include 
two-dimensional continuous wavelet transform (2D-CWT) analysis, fractal dimension estimation, and 
rugosity index calculation across various spatial scales. This package addresses the scarcity of 
open-source software for these sophisticated methods, which are crucial in modern terrain analysis, 
and facilitates data comparison and reproducibility. In the [software respository](https://github.com/GeoLarryLai/pyTopoComlexity.git), 
we also include a Jupyter Notebook file that integrates components from the Python-based 
surface-process modeling platform **Landlab** [@Hobley2017]. This allows researchers to 
simulate the smoothing of topography over time through terrestrial nonlinear hillslope 
diffusion processes. By combining these features, **pyTopoComplexity** advances the toolset 
available to researchers for measuring and simulating the time-dependent persistence of 
topographic complexity signatures against environmental forces on terrain surfaces.

@@

Here, $\mathbf{S} = -\nabla z$ represents the downslope topographic gradient, and $S$ is its magnitude. The parameter $K$ is a diffusion-like 
transport coefficient with dimensions of length squared per time. The simulation also incorporates the critical slope gradient ($S_c$) to 
ensure numerical stability and prevent the numerical instability when $S = S_c$. $N$ denotes the number of terms in the Taylor 
expansion, while $i$ specifies the number of additional terms included. If $N = 0$, the expression simplifies to linear diffusion [@Culling1963]. 
The default is set to $N = 2$ that gives the behavior described in @Ganti2012 as an approximation of the nonlinear diffusion.
